The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-04-01 reviews/disc-ac2.tex
Add minor corretions from Arjen to responses
Add manuscript quotes (work in progress)

\def\doi#1{doi:\allowbreak\href{http://dx.doi.org/#1}{#1}}
\def\referee#1{\bigskip\textcolor{journalname}{\textit{#1}}}

@@

Although we do not believe that bedrock elevation must have been in equilibrium with the ice sheet configuration at the LGM, we recognize that through our simplistic palaeoclimatic approach, isostatic effects are another significant source of error on modelled ice surface elevation, which we omitted to discuss in our manuscript.

In general, it became clear to us through your comments that we need more details about computation of bedrock deformation and its effects in the manuscript. These will surely be added in the revised version.

@@

Thank you for noticing this mistake. We will correct it.

>>>>

\def\doi#1{doi:\allowbreak\href{http://dx.doi.org/#1}{#1}}
\def\referee#1{\bigskip\textcolor{journalname}{\textit{#1}}}
\def\msquote#1{\begin{quote}\textit{#1}\end{quote}}

@@

To clarify our methods, we have added the following paragraph:

\msquote{Sea level is lowered by 120\,m and basal topography responds to ice load following a bedrock deformation model that includes point-wise isostasy, elastic lithosphere flexure and viscous mantle deformation in a~semi-infinite half-space \citep{lingle-clark-1985,bueler-etal-2007}. It uses a lithosphere density of 3300\,kg\,m$^{-3}$, a flexural rigidity of $5 \times 10^{24}$\,N\,m and a mantle viscosity of $1 \times 10^{21}$\,Pa\,s. Due to the high mantle viscosity, there exists a time lag between ice sheet growth and isostatic bedrock response. Because the distribution of marine sediments is assumed constant throughout the run, the till friction angle $\phi$ is not affected by changes in bed elevation.}

Although we do not believe that bedrock elevation must have been in equilibrium with the ice sheet configuration at the LGM, we recognize that through our simplistic palaeoclimatic approach, isostatic effects are another significant source of error on modelled ice surface elevation.

\msquote{The bedrock deformation model uses homogeneous lithospheric properties and a semi-infinite mantle of constant viscosity. Thus, it does not represent lateral variations of crustal and mantle properties characteristic of tectonically active margins such as the American Cordillera, nor does it include influence from the neighbouring Laurentide ice sheet. These limitations should be acknowledged when interpreting ice surface elevation and volume reconstructions presented in this study.}

In general, it became clear to us through your comments that we need more details about computation of bedrock deformation and its effects in the manuscript. These have been added in the revised version.

@@

Thank you for noticing this mistake. We have corrected it.
